%-------------------------
% Resume in LaTeX
% Author: Adam Abdulkadir
% Compatible with Overleaf (pdflatex)
%-------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{needspace}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.4in}
\addtolength{\evensidemargin}{-0.4in}
\addtolength{\textwidth}{0.8in}
\addtolength{\topmargin}{-.4in}
\addtolength{\textheight}{0.8in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \needspace{6\baselineskip}%
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\samepage}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Adam Abdulkadir} \\ \vspace{4pt}
    \small Software Engineer $|$ Charlotte, NC \\ \vspace{4pt}
    \small 703-364-8616 $|$
    \href{mailto:adama1862@outlook.com}{\underline{adama1862@outlook.com}} $|$
    \href{https://linkedin.com/in/adam-abdulkadir}{\underline{LinkedIn}} $|$
    \href{https://github.com/aabdulk862}{\underline{GitHub}} $|$
    \href{https://adam-abdul.com/}{\underline{Portfolio}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{Software Engineer supporting a high-volume distributed communications platform consisting of 40+ Java 21 and Spring Boot microservices processing millions of messages daily. Experienced diagnosing production incidents end-to-end, from CloudWatch analysis and root-cause investigation through deployment validation and rollback planning. Experience spans backend services, event-driven architectures (Kafka, RabbitMQ), cloud infrastructure on AWS EKS, SQL performance tuning, enterprise security remediation, and full-stack development using React and Angular.}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {George Mason University}{Fairfax, VA}
      {B.S. in Information Technology \textnormal{$|$} Minor in Business}{Aug 2017 -- Dec 2023}
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{AWS Certified Solutions Architect -- Associate} \hfill Aug 2023 \\
        \textbf{CompTIA Security+} \hfill Jan 2023 \\
        \textbf{Microsoft Azure Fundamentals} \hfill Oct 2024
    }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Infosys (Client: Charter Communications/Spectrum)}
      {Charlotte, NC}
      {Software Engineer}
      {Mar 2025 -- Present}
    \resumeItemListStart
        \resumeItem{Resolved production incidents on a communications platform processing millions of records daily across Email, SMS, RCS, and IVR channels — 40+ Java 21/Spring Boot microservices, Kafka, RabbitMQ, MariaDB, deployed on EKS.}
        \resumeItem{Diagnosed and fixed a production NPE silently dropping \textasciitilde16,000 messages/hour by tracing failures across async execution boundaries and identifying crash vectors in MapStruct-based event mapping logic — wrote 7 targeted tests using real prod payloads, deployed fix across East/West clusters.}
        \resumeItem{Resolved a multi-row query conflict caused by RCS channel fallback creating duplicate records — delivered a zero-downtime SQL fix validated against live prod data, and coordinated props-only deployment across 7 environment-specific config files.}
        \resumeItem{Designed and implemented a cross-service error categorization system spanning 3 microservices (CPM, Ingestion API, Publisher) — built a DB-backed category resolver with Spring cache integration, modified 30+ call sites, and enabled BI analytics on \textasciitilde9.7M annual error records previously uncategorized.}
        \resumeItem{Extracted Appointment Service from a monolithic codebase into a standalone Spring Boot microservice handling technician dispatch and appointment lifecycle via REST APIs and RabbitMQ — removed unused Kafka, S3, and batch dependencies, presented working demo to Director of Engineering.}
        \resumeItem{Managed full release lifecycle: wrote MOPs, bumped image versions across 15+ ArgoCD values files, coordinated UAT/prod deployments (East/West), authored rollback procedures, and ran post-deploy CloudWatch validation queries.}
        \resumeItem{Designed and built an AI-augmented engineering workflow: created a verified knowledge base covering 40+ microservices as structured context for LLM tools, authored custom steering files for code generation, and designed a CI pipeline to detect documentation drift when service code changes.}
      \resumeItemListEnd


\resumeSubheading
  {Revature}{Remote}
  {Full Stack Developer (Hire-Train-Deploy Program)}{Jun 2024 -- Mar 2025}
  \resumeItemListStart
    \resumeItem{Completed Revature's full-time Hire-Train-Deploy (HTD) software engineering program focused on Java, Spring Boot, React, PostgreSQL, Docker, Jenkins, and AWS cloud fundamentals.}
    \resumeItem{Successfully graduated a highly selective cohort where 11 of 29 trainees completed the program and qualified for client placement opportunities.}
    \resumeItem{Built and deployed full-stack applications including an Employee Reimbursement System (ERS) featuring JWT authentication, role-based access control, approval workflows, REST APIs, and PostgreSQL persistence.}
    \resumeItem{Developed backend services and frontend interfaces using Spring Boot and React while applying Agile methodologies, CI/CD practices, automated testing, and containerized deployments.}
    \resumeItem{Earned placement with Infosys following program completion, transitioning into enterprise software development supporting large-scale distributed systems and production environments.}
  \resumeItemListEnd

    \resumeSubheading{Global Association of Muslim Eritrean Communities (GAMEC)}{Remote}{Web Developer}{Aug 2023 -- Mar 2025}
    \resumeItemListStart
      \resumeItem{Designed and built the organization's public website from scratch using HTML, CSS, JavaScript, and Netlify, owning architecture decisions, deployment, and ongoing maintenance as the sole technical contributor.}
      \resumeItem{Led a full-stack migration from static HTML/jQuery to Astro 5 with React islands, introducing a component-based architecture, eliminating runtime dependencies, and reducing client-side JavaScript to zero on non-interactive pages.}
      \resumeItem{Implemented build-time rendering for 20+ pages, automated image optimization (WebP conversion), critical CSS inlining, XML sitemap generation, and structured data (JSON-LD), improving Core Web Vitals and SEO performance.}
      \resumeItem{Developed responsive layouts, WAI-ARIA–compliant navigation with full keyboard support, and progressive enhancement patterns across mobile and desktop experiences.}
    \resumeItemListEnd


    \resumeSubheading
      {Crocodile Solutions}{Remote}
      {Frontend Developer}{Apr 2023 -- Jul 2023}
      \resumeItemListStart
        \resumeItem{Migrated legacy applications to React/Next.js SPAs with Material UI, integrating with backend REST APIs and collaborating with backend engineers on API contract design.}
        \resumeItem{Built reusable React components and standardized routing, state management, and error handling patterns across multiple client applications.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
        \textbf{Backend:} Java 21, Spring Boot, Spring Batch, Spring Cloud Config, MapStruct, Resilience4j, JDBC, Kafka, RabbitMQ \\
        \textbf{Cloud \& Infrastructure:} AWS (EKS, CloudWatch, S3, Pinpoint), Docker, Kubernetes, ArgoCD, Helm, Linux, GitLab CI/CD, Jenkins \\
        \textbf{Databases:} MariaDB (Galera Cluster), PostgreSQL, Oracle, SQL Server \\
        \textbf{Observability:} CloudWatch Log Insights, Splunk, Qualys, structured logging, production debugging \\
        \textbf{Frontend:} React, TypeScript, Angular, Next.js, JavaScript, HTML/CSS, Material UI \\
        \textbf{Tools:} Git, GitLab, Gradle, Maven, IntelliJ, Postman, Confluence, Jira \\
        \textbf{Practices:} Microservices, Event-Driven Architecture, REST API Design, CI/CD, Rolling Deployments, Incident Response
    }}
\end{itemize}

%-------------------------------------------
\end{document}
